---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Changing neighborhoods, shifting connections: mapping relational geographies of gentrification using social media data."
```

# Changing neighborhoods, shifting connections: mapping relational geographies of gentrification using social media data
[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/atepoorthuis/relationalgeographiesofgentrification/master?urlpath=rstudio)
[![DOI](https://zenodo.org/badge/283771059.svg)](https://zenodo.org/badge/latestdoi/283771059)

This repository contains the data and code for our paper "Changing neighborhoods, shifting connections: mapping relational geographies of gentrification using social media data". The structure of this folder has been created with [rrtools](https://github.com/benmarwick/rrtools).


This repository contains the data and code for our paper:

> Poorthuis, A, T. Shelton and M. Zook, (2021). _`r Title`_. Urban Geography. Online at <http://dx.doi.org/10.1080/02723638.2021.1888016>


Our pre-print is online here:

> Poorthuis, A, T. Shelton and M. Zook, (2021). _`r Title`_. Urban Geography, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://osf.io/preprints/socarxiv/eq6vm/>


## Contents

This repository contains all the data and code needed to reproduce the
results and figures in our paper.

  - [analysis/01-prepare-twitter-data.Rmd](analysis/01-prepare-twitter-data.md):
    Prepare the Twitter data for subsequent analysis. Because of Twitter's terms and condition, we cannot share the raw Twitter data. However, all aggregated data necessary for reproducing the work in this paper is included.
  - [analysis/02-figures.Rmd](analysis/02-figures.md):
    This contains all the analytical and visualization steps needed to reproduce each figure in our analysis.
  - [figures/](figures/):
    Contains a high-resolution version of the figures in the paper. Unfortunately, the published version in *Urban Geography* contains only a down-sampled low-resolution version, which can make some of the figures difficult to read.

## How to download or install

You can download the compendium as a zip from from [this URL](https://github.com/atepoorthuis/relationalgeographiesofgentrification/archive/master.zip)

Or you can install this compendium as an R package, relationalgeographiesofgentrification, from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("atepoorthuis/relationalgeographiesofgentrification")
```

## Licenses

Text + figures and data:  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

Code: See the [DESCRIPTION](DESCRIPTION) file

